---
title: "My First Report"
author: "Nguyen Hoang Minh Vuong"
format:
  html:
    embed-resources: true
---

## Welcome to your practice report

This is a **Quarto** document. It mixes ordinary writing with live code, so your
report and your analysis always stay in sync. When you click **Render**, Quarto
runs the code below and builds a finished HTML page.

Try it now: change `author: "Your Name"` in the header above to your own name,
then click **Render**.

## A first look at the data

The code chunk below reads a small practice dataset from the `data/` folder and
shows the first few rows.

```{r}
patients <- read.csv("data/patients.csv")
head(patients)
```

## A first chart

```{r}
hist(patients$age,
     main = "Age distribution of practice patients",
     xlab = "Age (years)",
     col  = "steelblue")
```

## Your turn

- Add a sentence here describing what you notice in the chart.
- Render again and check that both your sentence and the chart appear.

When you are happy with the result, **commit and sync** your work (the Week 2
course page walks you through this), then submit your repository link on Canvas.

## My Notes 

# Task of *Assignment 1: Modern Workflow*
What I learned to day in class:
- How to create my repository using Fork
- How to edit README and other files in Codespace
- How to render the **Quarto** document to a specific type: html & pdf
- I know how to commit changes, and push it to save to my repository
- I know how to stop Codespace

# My Code

A sample code sell run by professor 
```{r}
summary(patients)
```

My simple R code
```{r}
# simple math
7 + 7

# print simple variable
name <- "Vuong"
age <- 18

name 
age
```